
\section{Future Work}

\begin{itemize}
    \item {
        The fundamental issue that was found while developing this project was the lack of appropriate data with appropriate annotations. 
        The first future task should be the retrieval and labeling of lots of data.
    }
    \item {
        The detector is the cornerstone of a tracker, further improvement should be done in this component.
    }
    \item {
        This work was done oriented towards the \ac{SORT} model and its successors, all of them are online and causal. 
        Some research should be considered in other tracking architectures (for instance, the models in the papers \cite{10016298} and \cite{luo2023realtime}). Highlighting bidirectional trackers and fully data driven trackers.
    }
    \item {
        Our current results are tracks, the \ac{CSIC} researchers needs some mean to evaluate the certainty of a track; or, in the best case, the certainty improvement for a subset of ants.
        A future work should try to research and develop the ``certainty on tracks" topic.
    } 
    \item {
        The appearance model was unsuccessful; however, it still has the potential to be a powerful tool in ants tracking. 
        A further research on models and trainings should be continued. However, new data has to be acquired and labeled before it can be started.
    } 
    \item {
        As stated in the introduction, after obtaining enough data, post processing data driven model for traking should be researched. Starting with the AFLink from Strong SORT.
    } 
    \item {
        The development of an ant behavior model is being done in parallel with this work. 
        Once the model is available, it should be a task to test its performance by including it on the tracker.
    } 
\end{itemize}
